% mnras_guide.tex
% v3.1 released 11 June 2020
% Keith T. Smith (Royal Astronomical Society)
\documentclass[fleqn,usenatbib,useAMS]{mnras}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages

\input{ mnras_packages}


%%%%%% Don't change these lines
\input title
\begin{document}
%\label{firstpage}
%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
%\input abstract
%%%%%%

So you have to write a talk.  Bake these things into your preparation and
delivery.

\begin{enumerate}
    \item You are talking to the audience.
        \begin{enumerate}
            \item Get in their heads before you start.
                \begin{enumerate}
                    \item How much do they need you to introduce?
                    \item How high up the mountain can you get?
                    \item They don't care until you tell them to care.
                    \item They might be smarter than you.  Don't talk down.
                \end{enumerate}
            \item Look at them.
                \begin{enumerate}
                    \item They're scary.  Don't look away.
                    \item They will tell you how you're doing with their faces.
                        ADAPT.
                    \item Do they still care?  That's your job.
                \end{enumerate}
        \end{enumerate}
    \item You're telling a story. That is all.
        \begin{enumerate}
            \item The whole flight path is laid out at the start.  Context,
                Work, Purpose.
            \item Everything you say connects to the start.  
            \item Everything you say connects to the end.
            \item Everything you say connects to what you just said.  No
                whiplash.
            \item Everything you say connects to what you're saying next.  Guide
                the way.
            \item It's not a majic show.  Nobody is amazed if you pull something
                out of your hat.
            \item Socks then shoes.  Order matters.
        \end{enumerate}
    \item Introduce every plot.  It takes people a second to spin up.
        \begin{enumerate}
            \item Declare the axes.
            \item Declare what data/eqns are in the plot.
            \item Describe the lines and colors
            \item Why is this plot here?  Needs to be obvious or stated.
        \end{enumerate}
    \item Repeating yourself drives the point home.
    \item One idea per slide.
    \item You want them to listen, not read. Only enough text to remind you what
        to say, and remind them what you just said.
    \item Don't say two words when one works.
    \item Say all nine words you need.
\end{enumerate}

%optional.
%\input mnras_toc

%\input introduction

%%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
%
%\bibliographystyle{mnras}
%\bibliography{main.bib} % if your bibtex file is called example.bib
%
%
%
%% Don't change these lines
%\bsp	% typesetting comment
%\label{lastpage}
\end{document}

% End of mnras_guide.tex
